### 2017-11-22 Docs/Thesis/docs/chapter1.tex
updates

It is already a well-known fact that the type of traffic used on performing tests matters. Studies show that a realistic Ethernet traffic provides a different and more variable load characteristics on routers\cite{harpoon-validation}, even with the same mean bandwidth consumption. It indicates that tests with constant bit rate traffic generator tools are not enough for a complete validation of a new technology. There are many reasons for this behavior, which includes burstiness and packet sizes.

A burstier traffic can cause packet more buffer overflows on network \cite{burstiness-queue-lenght} \cite{modelling-of-self-similar} \cite{empirical-interarrival-study}, degenerating network performance\footnote{Fuatures such as packet-trains periods and inter-packet times affect traffic burstiness}. Also, a burstier and realistic traffic will not just impact on performance, but on measurement accuracy as well \cite{legotg-paper} \cite{background-traffic-matter}. Another key question is how applications will deal with packets. It is a well-known fact that applications have a huge performance degradation processing small packets\cite{comparative-trafficgen-tools}. A synthetic realistic traffic must not have a single packet-size, but must use a distribution \cite{packet-distribution-model}.

@@

Since on traditional hardware-based types of \textit{middleboxes}, the impact of realistic traffic is not negligible, we can expect that its impact over virtualized middle-boxes should be even larger, due the extra overhead of a virtualization layer.

Another important point is the flow-oriented operation of SDN networks. Each new flow arriving on a SDN switch demands an extra communication load between it and the controller. This may create a bootleneck between the switch and the controller.  We also have a flow-oriented operation on SDN switches. Since its operation relies on queries on flow tables, a stress load must have the same flow properties of an actual ISP scenario.

>>>>

It is already a well-known fact that the type of traffic used on performing tests matters. Studies show that a realistic Ethernet traffic provides a different and more variable load characteristics on routers\cite{harpoon-validation}, even with the same mean bandwidth consumption. It indicates that tests with constant bit rate traffic generator tools are not enough for a complete validation of new technologies. There are many reasons for this behavior, which includes burstiness and packet sizes.

A burstier traffic can cause packet more buffer overflows on network \cite{burstiness-queue-lenght} \cite{modelling-of-self-similar} \cite{empirical-interarrival-study}, degenerating network performance\footnote{Fuatures such as packet-trains periods and inter-packet times affect traffic burstiness}. Also, a burstier and realistic traffic will not just impact on performance, but on measurement accuracy as well \cite{legotg-paper} \cite{background-traffic-matter}. Another key question is how applications will deal with packets. It is a well-known fact that applications have a huge performance degradation processing small packets\cite{comparative-trafficgen-tools}. A realistic synthetic traffic must not have a single packet-size but must use a distribution \cite{packet-distribution-model}.

@@

Since on traditional hardware-based types of \textit{middleboxes}, the impact of realistic traffic is not negligible; we can expect that its impact over virtualized middle-boxes should be even larger, due the extra overhead of a virtualization layer.

Another critical point is the flow-oriented operation of SDN networks. Each new flow arriving on an SDN switch demands an extra communication load between it and the controller. This may create a bottleneck between the switch and the controller.  We also have a flow-oriented operation on SDN switches. Since its operation relies on queries on flow tables, a stress load must have the same flow properties of an actual ISP scenario.
